% %%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PRELUDE (NOT RENDERED)
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[sfdefault]{noto-sans}

\makeatletter
\DeclareRobustCommand*{\https}{\hyper@normalise\https@}
\def\https@#1{\underline{\lowercase{\hyper@linkurl{\Hurl{#1}}{https://#1}}}}
\DeclareRobustCommand*{\mailto}{\hyper@normalise\mailto@}
\def\mailto@#1{\underline{\lowercase{\hyper@linkurl{\Hurl{#1}}{mailto:#1}}}}
\makeatother

\pagestyle{fancy}
\fancyhf% % clear all header and footer fields
\fancyfoot%
\setlength{\footskip}{4.09pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
 
\raggedbottom%
\raggedright%
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule{} \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

\newcommand{\sharplang}[1]{%
    {\settoheight{\dimen0}{#1}#1\kern-.05em \resizebox{!}{\dimen0}{\raisebox{\depth}{\#}}}%
}
\newlist{sectionList}{itemize}{1}%
\setlist[sectionList]{%
    leftmargin=0.15in, 
    label={}
}%

\newlist{itemList}{itemize}{1}%
\setlist[itemList]{%
    leftmargin=10pt, 
    before=\small,
    after=\vspace{-5pt}, 
    label={\textbullet},
    itemsep=1pt
}%

\newlist{skillList}{description}{1}%
\setlist[skillList]{%
    itemsep=1pt,
    labelindent=12pt,
    parsep=0pt,
    before=\small,
    after=\vspace{-5pt}
}

\newcommand{\placeblock}[4]{%
    \vspace{-2pt}\item%
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}%
        \textbf{#1} & #2 \\%
        \textit{\small#3} & \textit{\small #4} \\%
    \end{tabular*}\vspace{-7pt}%
}%

\newenvironment*{place}[4]{%
    \placeblock{#1}{#2}{#3}{#4}
    \begin{itemList}
}{%
    \end{itemList}
}%

\newenvironment*{project}[2]{%
    \item%
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}%
		\small#1 & #2 \\%
	\end{tabular*}\vspace{-7pt}%
    \begin{itemList}%
    }{%
    \end{itemList}%
}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%
% IDENTIFYING INFORMATION MACROS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\myname}{Greg Rosenbaum}
\newcommand{\myphone}{+972 54-328-3246}
\newcommand{\myemail}{work.gregr@gmail.com}
\newcommand{\mygithub}{GregRos}
\newcommand{\mylinkedin}{greg-ros}
\newcommand{\mywebsite}{career.gregros.dev}

\newcommand{\eternitech}{Eternitech}
\newcommand{\reflectiz}{Reflectiz}
\newcommand{\appdome}{Appdome}

\newcommand{\parjs}{Parjs}
\newcommand{\imms}{Imms}

\newcommand{\technion}{Technion}

\newcommand{\ramatgan}{Ramat Gan, Israel}
\newcommand{\telaviv}{Tel Aviv}
\newcommand{\haifa}{Haifa, Israel}
\newif\ifanon%

\ifanon%
\renewcommand{\myname}{My Name}
\renewcommand{\myphone}{+972 XX-XXX-XXXX}
\renewcommand{\myemail}{work.gregr@gmail.com}
\renewcommand{\mywebsite}{career.my-site.dev}
\renewcommand{\mygithub}{my-github}
\renewcommand{\mylinkedin}{www.linkedin.com/in/my-linked-in}
\renewcommand{\eternitech}{CompanyA}
\renewcommand{\reflectiz}{CompanyB}
\renewcommand{\appdome}{CompanyC}

\renewcommand{\parjs}{parser-lib}
\renewcommand{\imms}{collection-lib}

\renewcommand{\technion}{Top Institution}

\renewcommand{\ramatgan}{Place1}
\renewcommand{\telaviv}{Place2}
\renewcommand{\haifa}{Place3}
\fi

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%
% HEADER STRUCTURE
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\header}{%
    \begin{center}
        \textbf{\Huge \normalshape{} \myname} \\
        \vspace{1pt}
        \small \myphone{} $|$ \mailto{\myemail} $|$
        \https{\mywebsite} $|$
        \https{linkedin.com/in/greg-ros}
    \end{center}%
}

\newcommand{\tagline}{%
    \begin{center}
        \vspace{-5pt}
        \small \textit{I love building things.}
        \vspace{-20pt}
    \end{center}
}
\newenvironment{jobReflectizLead}{%
    \begin{place}{Tech Lead}{Jan 2021 -- Present}{\reflectiz}{\ramatgan}
}{%
    \end{place}
}
\newenvironment{jobAppdome}{%
    \begin{place}{Senior Backend Developer}{Jul 2019 -- Oct 2020}{\appdome}{\telaviv}
}{
    \end{place}
}
\newenvironment{jobReflectizDev}{%
    \begin{place}
        {Senior Backend Developer}{May 2017 -- Feb 2019}
        {\reflectiz}{\ramatgan}
}{%
    \end{place}
}

\newenvironment{jobEternitech}{%
    \begin{place}{Full Stack Developer}{Jan 2016 -- May 2017}
        {\eternitech}{\ramatgan}%
}{%
    \end{place}
}
\begin{document}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DOCUMENT START
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\header%
\tagline%

\section{Experience}
\begin{sectionList}
 
    \begin{jobReflectizLead}
        %\item Broad technological leadership role reporting directly to company founders.
        \item Provided technical leadership and guidance to multiple teams.
        \item Led development of browser-based platform in TypeScript on Node.js.
        \item Solved architectural problems at every level of scale, crossing stack boundaries.
        \item Translated business requirements to research objectives and development roadmaps.
        \item Designed numerous APIs following functional programming principles.
        \item Fostered a culture of code quality, testing, and documentation.
        \item Led integration of IaC, experimental protocols, and new architectural components.
        \item Set up development workflows involving issue tracking, code reviews, and CI/CD.
        %\item Directed research into browser automation, monitoring, and control.
        %\item Ported existing infrastructure to IaC, scaled by \texttimes30+, and expanded into new regions.
        %\item Translated business requirements to research objectives and development roadmaps.
        %\item Designed a data pipeline processing 100+ MB/sec of graph data.
        \item Wrote tools, scripts, and packages scripts in Python and Bash, used across multiple teams.
        %\item Deployed cloud networking solutions and complex machine-specific network configurations.
        \item Led deployment of system health and throughput metrics across 100+ instances of 10+ services.
        %\item Extensive research into the massive Chromium codebase (C++).
        %\item Developed high performance component in Rust used in internal processes.
        %\item Set conventions and conducted code reviews across multiple codebases.
        %\item Wrote CLI tools and microservices used by multiple teams built on a backbone of NPM packages.
        %\item Company-wide technological leadership role reporting directly to company founders.
        %\item Wrote 10+ micro-services and CLI tools in Python and Bash used across multiple teams.
        %\item Integrated observability into 100+ spot instances to understand incidents post mortem.
        %\item Opimized compute infrastructure for throughput vs cost running perf-sensitive workloads.
        %\item Hacked together a framework for domain-specific integration tests, used to write 100+ test cases.
     \end{jobReflectizLead}

    \begin{jobAppdome}
        \item Solved scalability, dependency, migration, performance, and memory issues in Node.js.
        \item Modernized development processes by introducing PRs and code reviews.
        %\item Designed automation API based on a graphical user interface, for use by clients.
        \item Continuously refactored codebase in line with best practices.
        \item Participated in feature design, specification, and testing.
    \end{jobAppdome}

    \begin{jobReflectizDev}
        \item Built Chromium-based platform$^\star$ in TypeScript on Node.js.
        \item Wrote code monitoring all browser activity, including JS, HTML, CSS, Web APIs, iframes, HTTP, etc.
        \item Flexible program architecture allowed company to pivot based on market opportunities.
        \item Leveraged multi-process parallelism for throughput and consistency in perf-sensitive workloads.
        \item Designed a testable program architecture with strong SoC, using DI for loose coupling.
    \end{jobReflectizDev}
    \begin{jobEternitech}
        \item Built SPAs for clients with \sharplang{C}, Node.js backends, React frontend, and MSSQL.\@
        \item Maintained existing apps using ASP.NET (MVC/Web Forms), JQuery, Classic ASP, etc.
        \item Gathered requirements, wrote specifications, received feedback, provided support, etc.
    \end{jobEternitech}
\end{sectionList}%


%-----------PROJECTS-----------
\section{Projects}
\begin{sectionList}%
    \begin{project}{\textbf{\parjs} $|$ \emph{TypeScript, JavaScript} $|$ \https{\mywebsite/parjs}}{2018 -- Present}
        \item Developed parser building library following the parser combinator pattern, e.g. Parsec (Haskell).
        \item Hand-wrote 50+ parsers and combinators, plus a separate package for Unicode char recognition.
        \item Library is popular in its domain with 16K+ monthly downloads and multiple active contributors.
    \end{project}
    \begin{project}{\textbf{\imms} $|$ \emph{\sharplang{C}, \sharplang{F}} $|$ \https{\mywebsite/imms}}{2012 -- 2016}
        \item High performance immutable collection library in \sharplang{C}, rigorously tested in \sharplang{F}.
        \item Achieved optimal complexity by taking data structures and algorithms from research papers.
        \item Maximized performance using low-level optimizations via benchmarking and CPU profiling.
    \end{project}
\end{sectionList}%

\section{Skills}
\begin{skillList}
    \item[Spoken:] English (native), Hebrew (native)
    \item[Written:] TypeScript, JavaScript, Python, Bash, \sharplang{C}, \sharplang{F}, C++, Scala, Kotlin, Rust, \LaTeX, \dots
    \item[Platforms:] Node.js, .NET, Linux, Windows, Azure, GCP, K8s, Docker, \dots
    \item[Databases:] MSSQL, PostgreSQL, MongoDB, Memgraph
\end{skillList}

\section{Education}
\begin{sectionList}%
    \placeblock{BSc in Computer Science (Incomplete)}{2013 -- 2015}{\technion}{\haifa}
\end{sectionList}

%-------------------------------------------
\end{document}%
