


\newcommand{\RefDistributed}{%
    \item Designed a stateless, distributed system that scaled to 300+ concurrent automation jobs based on demand.
}%
\newcommand{\RefLeadership}{%
    \item Provided technical leadership and guidance to multiple teams and mentored developers.
}%
\newcommand{\RefDesignedPlatform}{%
    \item Designed browser automation platform at the core of the product.
}%
\newcommand{\RefChromiumModifications}{%
    \item Designed a set of targeted modifications to the Chromium browser.
}%
\newcommand{\REfIaCExpansion}{%
    \item Ported infrastructure to IaC and rapidly expanded into 7 regions, enabling the acquisition of new clients.
}%
\newcommand{\RefSystemObservability}{%
    \item Integrated observability across 300+ instances of 10+ services, allowing for rapid incident response.
}%
\newcommand{\RefMicroservicesTools}{%
    \item Wrote micro-services and tools in Python and Bash for complex tasks, accelerating development.
}%
\newcommand{\RefCloudNetworkingSolutions}{%
    \item Deployed cloud networking solutions and complex machine network configurations.
}%
\newcommand{\RefWebProtocolsResearch}{%
    \item Led research into web protocols, client-side technologies, and web browsers.
}%

\newcommand{\RefStatelessRPCInterface}{%
    \item Designed a stateless RPC interface for a distributed system.
}%
\newcommand{\RefGraphTheoryASTs}{%
    \item Leveraged graph theory, walked ASTs, and designed a language for browser automation.
}%
\newcommand{\RefChromiumCodebaseResearch}{%
    \item Extensive research into the massive Chromium codebase (C++).
}%
\newcommand{\RefBrowserAutomationResearch}{%
    \item Directed research into browser automation, monitoring, and control.
}%
\newcommand{\RefOptimizedRecursive}{%
    \item Wrote recursive queries in MSSQL, extracting additional value from existing data.
}%
\newcommand{\RefOptimizedDataArch}{%
    \item Optimized database structure using indexing and partioning, reducing query times by 10x.
}

\newcommand{\RefDataPipeline}{%
    \item Designed robust microservice-based pipeline, improving throughput by 5x and fail rate by 90\%.
}%
\newcommand{\RefDataArch}{%
    \item Optimized MSSQL architecture
}
\newcommand{\RefCLIToolsAndMicroservices}{%
    \item Wrote CLI tools and microservices used by multiple teams built on a backbone of NPM packages.
}%
\newcommand{\RefIntegrationTestFramework}{%
    \item Hacked together a framework for domain-specific integration tests, used to write 100+ test cases.
}%
\newcommand{\RefDevelopmentWorkflows}{%
    \item Set up development workflows involving issue tracking, code reviews, and CI/CD.
}%

\newcommand{\RefCodeReviewsAndConventions}{%
    \item Set conventions and conducted code reviews across multiple codebases.
}%
\newcommand{\RefDeployedInfrastructure}{%
    \item Deployed infrastructure through mastery of GCP, K8s, and IaC tools.
}%
\newcommand{\RefContainerizedAndOrchestrated}{%
    \item Containerized and orchestrated services, and set up CI/CD pipelines.
}%

\newcommand{\RefResearchedAndAppliedTech}{%
    \item Researched and applied technologies such as Rust, WebAssembly, and graph databases.
}%

\newcommand{\RefOptimizedCompute}{%
    \item Opimized compute infrastructure for throughput vs cost running perf-sensitive workloads.
}%

\newcommand{\RefIntegratedIaCAndProtocols}{%
    \item Led integration of IaC, experimental protocols, and new architectural components.
}%

\newcommand{\RefChromiumBasedPlatform}{%
    \item Built Chromium-based platform$^\star$ in TypeScript on Node.js.
}%
\newcommand{\RefBrowserMonitoring}{%
    \item Developed monitoring layer for all webpage-based activity, forming the backbone of the product.
}%

\newcommand{\RefMultiProcessParallelism}{%
    \item Leveraged multi-process parallelism to better utilize system resources, reducing costs.
}%
\newcommand{\RefTestableProgramArchitecture}{%
    \item Designed a testable program architecture with strong SoC, using DI for loose coupling.
}%

\newcommand{\RefLedResearchBrowser}{%
    \item Led research into side-effect free browser automation, monitoring, and control.
}%
\newcommand{\RefMonitorBrowser}{%
    \item Worked closely with web specifications to design monitoring for all browser activity.
}%

\newcommand{\RefDevRoadmaps}{%
    \item Translated business requirements to research objectives and development roadmaps.
}%
\newcommand{\RefDebugging}{%
    \item Extensive debugging of minified bundles and obfuscated code to resolve incidents.
}%
\newcommand{\RefLedResearch}{%
    \item Led research into web protocols, client-side technologies, and web browsers.
}%