% !TEX root = ../cvs/gr.nl.v1.tex

\newcommand{\ReffPivotalRole}{%
    \item Pivotal technical leadership position in a successful, rapidly growing client-side security company.
}
\newcommand{\ReffScaling}{%
    \item Took charge of a monolithic system and scaled it to 100+ instances spread across 7 regions.
}
\newcommand{\ReffArchitectureList}{%
    \item Designed highly scalable and cost-effective systems based on input from key stakeholders, including:
    \begin{itemize}
        \item Cost-effective data pipeline processing over 300 MB/s of graph data.
        \item Development and automation platform used by a team of developers.
        \item A network of interdependent packages that accelerated development times.
    \end{itemize}
}
\newcommand{\ReffWebResearch}{%
    \item Led research into experimental technologies for browser monitoring, automation, and control.
}%
\newcommand{\RefDistributed}{%
    \item Designed a stateless, distributed system that scaled to 300+ concurrent automation jobs based on demand.
}%
\newcommand{\ReffCommunicated}{%
    \item Effectively communicated complex architectural characteristics to cross-functional teams.
}

\newcommand{\ReffAccelerated}{%
    \item Accelerated development by:
    \begin{itemize}
        \item Increasing code reuse through refactoring existing codebases into a package architecture.
        \item Indentifying dev bottlenecks and writing automation tools to overcome them.
        \item Reviewing feature designs and specifications with an eye towards maintainability and scalability.
    \end{itemize}
}

\newcommand{\ReffAcquisitionClients}{%
    \item Enabled the acquisition of new clients by:
    \begin{itemize}
        \item Translating client demands into business requiments and research objectives.
        \item Leveraging IaC to expand into new regions.
        \item Participating in sales meetings with key clients as a technical expert.
    \end{itemize}
}
\newcommand{\ReffEmpowered}{%
    \item Empowered developers to make architectural decisions by:
    \begin{itemize}
        \item Translating domain-specific stakeholder concerns into software requirements.
        \item Fostering open discussion about existing shortcomings, future needs, and potential solutions.
        \item Providing technical guidance and mentoring.
    \end{itemize}
}
\newcommand{\ReffHandsOnTools}{%
    \item Hands-on development of tools and microservices in Python and Bash.
}
\newcommand{\ReffIncidentShort}{%
    \item Research into incidents post-mortem, including root cause analysis and remediation.
}
\newcommand{\ReffIncidents}{%
    \item Research into incidents post-mortem, including:
    \begin{itemize}
        \item Root cause analysis and remediation.
        \item Translating highly technical information into actionable items for cross-functional teams. 
        \item Drafted research findings for stakeholders and leaders -- with an eye towards promotional material.
    \end{itemize}
}
\newcommand{\ReffDocumentation}{%
    \item Produced extensive documentation, diagrams, architectural overviews, and technical specifications.
}
\newcommand{\ReffOptimized}{%
    \item Optimized RDBMS architecture using indexing and partitioning.
}
\newcommand{\ReffObservability}{%
    \item Used observability to ensure system performance and integrity by:
    \begin{itemize}
        \item Deploying a system-wide tracing solution, allowing for rapid incident response.
        \item Designing a suite of domain-specific system-wide metrics to monitor system health and performance.
        \item Building an accessible Grafana dashboard for cross-functional teams.
        \item Research into incidents post-mortem, including root cause analysis and remediation.
    \end{itemize}
}
\newcommand{\ReffCiCd}{%
    \item Set up CI/CD platforms and pipelines following GitOps principles:
    \begin{itemize}
        \item Deploying a system-wide tracing solution, allowing for rapid incident response.
        \item Designing a suite of domain-specific system-wide metrics to monitor system health and performance.
        \item Building an accessible Grafana dashboard for cross-functional teams.
        \item Research into incidents post-mortem, including root cause analysis and remediation.
    \end{itemize}
}