% !TEX root = ../cvs/gr.nl.v1.tex

\newcommand{\RefDevFoundational}{%
    \item Joined the startup as a foundational developer.
}%
\newcommand{\RefDevDevelopment}{%
    \item Single-handedly built the highly technical browser monitoring component at the core of the product:
    \begin{itemize}
        \item By performing intensive research into web protocols and client-side technologies.
        \item Working closely with the massive Chromium codebase. 
        \item Integrating experimental technologies into a robust, fault-tolerant, observable system.
        \item Flexible architecture allowed the company to pivot based on market opportunities.
    \end{itemize}
    \item Wrote complex SQL queries using recursion and other advanced techniques.
}%
\newcommand{\RefDevSQL}{%
    \item Wrote complex and optimized complex SQL queries in MSSQL.
    \begin{itemize}
        \item 
        \item Optimized database structure using indexing and partitioning, reducing query times by 10x.
}%

\newcommand{\RefDevOptimized}{%
    \item Optimized SQL queries based on query plans, ancient database lore, and the phases of the moon.
}%


\newcommand{\RefResearchedBrowser}{%
    \item Researched solutions in browser monitoring and control.
}%
\newcommand{\RefDevelopedBrowser}{%
    \item Developed browser-based platform for monitoring webpage activity.
}%
\newcommand{\RefFlexibleProgramArchitecture}{%
    \item Flexible program architecture allowed company to pivot based on market opportunities.
}%
\newcommand{\RefOptimizedQueries}{%
    \item Optimized SQL queries based on query plans, ancient database lore, and the distant motions of heavenly bodies.
}

