\documentclass[a4paper,11pt]{article}

\input{../utils/preamble.tex}
\input{../utils/names.tex}
\newcommand{\eternitech}{Eternitech}
\newcommand{\reflectiz}{Reflectiz \textemdash{}  SaaS }
\newcommand{\appdome}{Appdome \textemdash{}  SaaS}
\newcommand{\sentto}{v }

\input{../utils/jobenvs.tex}

\lhead{\small\color{gray}@\sentto}

\begin{document}
\header%
\section{Summary}
\begin{itemList}
    \item 8 years of delivering quality software using TypeScript, \sharplang{C}, Bash, and Python.
    \item 5 years of building and maintaining highly distributed systems.
    \item 8 years of working with multiple databases, including MSSQL, PostgreSQL, and MongoDB.
    \item A lifetime of programming.
\end{itemList}
\section{Experience}
\begin{sectionList}

    \begin{jobReflectizLead}
        \item Led research into side-effect free browser automation, monitoring, and control.
        \item Worked closely with web specifications to design monitoring for all browser activity.
        \item Translated business requirements to research objectives and development roadmaps.
        \item Provided technical leadership and guidance to multiple teams
        \item Extensive debugging sessions, working with minified bundles and obfuscated code.
        \item Designed and developed a browser automation platform in TypeScript on Node.js.
        \item Built a stateless, distributed system running 300+ concurrent automation jobs across 7 regions.
        \item Designed a set of targeted modifications to the Chromium browser.
        \item Built a data pipeline processing 100+ MB/sec of graph data.
        \item Integrated system-wide observability across 100+ instances of 10+ services.
        \item Wrote 10+ micro-services and CLI tools in Python and Bash used across multiple teams.
        \item Deployed cloud networking solutions and complex machine network configurations.
        \item Ported existing infrastructure to IaC and Kubernetes.

        % DOMAIN
        % \item Led research into web protocols, client-side technologies, and web browsers.
        % \item Developed a browser automation platform in TypeScript on Node.js.
        % \item Built a data pipeline processing 100+ MB/sec of graph data.
        % \item Designed a stateless RPC interface for a distributed system.
        % \item Integrated system-wide observability across 100+ instances of 10+ services.
        % \item
        % \item Leveraged graph theory, walked ASTs, and designed a language for browser automation.
        %\item Extensive research into the massive Chromium codebase (C++).
        %\item Directed research into browser automation, monitoring, and control.

        % % TOOLS
        % \item Optimized complex recursive queries in RDBMS (MSSQL).
        % % \item Applied mastery of TypeScript, client-side JavaScript, and Node.js to benefit products and systems.
        % % \item Successfuly integrated rxjs, monitoring, Rust, and IaC into the company's stack.
        % %\item Developed high performance component in Rust used in internal processes.
        % % \item Designed numerous APIs following functional programming principles.

        % \item Designed a stateless RPC interface for a distributed system.

        % % LEADERSHIP
        % %\item Provided technical leadership and guidance to multiple teams and mentored developers.
        % %\item Provided technical leadership and guidance to multiple teams and mentored developers.
        % % \item Fostered a culture of code quality, testing, and documentation.
        % %\item Company-wide technological leadership role reporting directly to company founders.

        % % ARCHITECTURE
        % % \item Solved architectural problems at every level of scale, crossing stack boundaries.
        % % \item Translated business requirements to research objectives and development roadmaps.
        % \item Worked on a stateless + distributed system, with 100+ instances across 7 regions running 10+ services.
        % \item Integrated system-wide observability across 100+ instances of 10+ services, plus grafana dashboards.
        % \item Built a data pipeline processing 100+ MB/sec of graph data.
        % \item Designed a stateless RPC interface for a distributed system.
        %

        % DEVEX
        % \item Wrote CLI tools and microservices used by multiple teams built on a backbone of NPM packages.
        %\item Hacked together a framework for domain-specific integration tests, used to write 100+ test cases.

        %  \item Set up development workflows involving issue tracking, code reviews, and CI/CD.
        %\item Wrote 10+ micro-services and CLI tools in Python and Bash used across multiple teams.
        %\item Set conventions and conducted code reviews across multiple codebases.

        % DEVOPS
        % \item Deployed infrastructure through mastery of GCP, K8s, and IaC tools.
        % \item Containerized and orchestrated services, and set up CI/CD pipelines.
        % \item Wrote 10+ micro-services and CLI tools in Python and Bash used across multiple teams.
        % \item Researched and applied technologies such as Rust, WebAssembly, and graph databases.
        %\item Ported existing infrastructure to IaC, scaled by \texttimes30+, and expanded into new regions.
        %
        %\item Opimized compute infrastructure for throughput vs cost running perf-sensitive workloads.
        %\item Integrated observability into 100+ spot instances to understand incidents post mortem.
        % \item Led integration of IaC, experimental protocols, and new architectural components.


    \end{jobReflectizLead}

    \begin{jobAppdome}
        \item Solved scalability, dependency, migration, performance, and memory issues in Node.js.
        \item Worked on internal components in Python and Golang.
        \item Modernized development processes by introducing PRs and code reviews.
        %\item Designed automation API based on a graphical user interface, for use by clients.
        %\item Continuously refactored codebase in line with best practices.
        \item Participated in feature design, specification, and testing.
    \end{jobAppdome}

    \begin{jobReflectizDev}
        \item Built Chromium-based platform$^\star$ in TypeScript on Node.js.
        \item Developed monitoring layer for most browser activity.
        \item Flexible program architecture allowed company to pivot based on market opportunities.
        \item Leveraged multi-process parallelism for throughput and consistency in perf-sensitive workloads.
        \item Designed a testable program architecture with strong SoC, using DI for loose coupling.
    \end{jobReflectizDev}
    \begin{jobEternitech}
        \item Built SPAs for clients with \sharplang{C}, Node.js backends, React frontend, and MSSQL.\@
        \item Maintained existing apps using ASP.NET (MVC/Web Forms), JQuery, Classic ASP, etc.
        \item Gathered requirements, wrote specifications, received feedback, provided support, etc.
    \end{jobEternitech}
\end{sectionList}%


%-----------PROJECTS-----------
\section{Projects}
\begin{sectionList}%
    \begin{project}{\textbf{\parjs} $|$ \emph{TypeScript, JavaScript} $|$ \https{\mywebsite/parjs}}{2018 -- Present}
        \item Developed parser building library following the parser combinator pattern, e.g. Parsec (Haskell).
        \item Hand-wrote 50+ parsers and combinators, plus a separate package for Unicode char recognition.
        \item Library is popular in its domain with 16K+ monthly downloads and multiple active contributors.
    \end{project}
    \begin{project}{\textbf{\imms} $|$ \emph{\sharplang{C}, \sharplang{F}} $|$ \https{\mywebsite/imms}}{2012 -- 2016}
        \item High performance immutable collection library in \sharplang{C}, rigorously tested in \sharplang{F}.
        \item Achieved optimal complexity by taking data structures and algorithms from research papers.
        \item Maximized performance using low-level optimizations via benchmarking and CPU profiling.
    \end{project}
\end{sectionList}%

%-------------------------------------------
\end{document}%
