\documentclass[a4paper,11pt]{article}

\input{../utils/_preamble.tex}
\input{../utils/_names.tex}
\newcommand{\eternitech}{Eternitech}
\newcommand{\reflectiz}{Reflectiz}
\newcommand{\appdome}{Appdome}
\newcommand{\sentto}{v }

\input{../utils/_eduenvs.tex}
\input{../utils/_jobenvs.tex}
\input{../points/_appdome.tex}
\input{../points/_eternitech.tex}
\input{../points/_ref.developer.tex}
\input{../points/_ref.architect.tex}
\begin{document}
\header%
\section{Experience}
\begin{sectionList}

    \begin{jobReflectizLead}
        \ReffPivotalRole
        \ReffScaling
        \ReffArchitectureList
        \ReffCommunicated
        \ReffObservability
        \ReffAcquisitionClients
        \ReffEmpowered
        \ReffIncidentShort
        \ReffAccelerated
        \ReffDocumentation
    \end{jobReflectizLead}

    \begin{jobAppdome}
        \AppSummaryTechLead
        \AppGuidedDevelopers
        \AppComplexTechnical
        \AppModernizedDevelopmentProcesses
        \AppMajorRefactoring
    \end{jobAppdome}

    \begin{jobReflectizDev}
        \RefDevFoundational
        \RefDevDevelopment
        \RefDevOptimized
    \end{jobReflectizDev}
    \begin{jobEternitech}
        \EtrSPAsForClients
        \EtrMaintainedExistingApps
        \EtrRequirementsAndSpecifications
    \end{jobEternitech}
\end{sectionList}%

\section{Education}
\begin{sectionList}
    \begin{eduTechnion}
    \end{eduTechnion}
\end{sectionList}%
%-----------PROJECTS-----------
\section{Own Work}
\begin{sectionList}
    \begin{project}{\textbf{\gregrosdev} $f|$ Blog $|$ \https{\mywebsite}}{2024 -- Present}
        \item Personal blog about web technology, software architecture, API design, and more.
        \item Conveys highly technical topics using an accessible and informal tone.
        \item Demonstrates deep understanding of software architecture and API design.
        \item Used marketing principles to grow readership and engagement.
        \item Hosted on [Platform]
    \end{project}
    \begin{project}{\textbf{\gregrosdev} $|$ Platform $|$ \https{\mywebsite}}{2024 -- Present}
        \item Extensible and performant content platform built using Next.js and other leading web techs.
        \item Achieved by learning modern libraries, tools, and frameworks on the spot.
        \item Integrated marketing staples like Google Analytics, SEO, and social.
        \item Deployed via CD on Perdido K8S cluster.
    \end{project}    
    \begin{project}{\textbf{perdido}}{2022 -- Present}
        \item Enterprise-grade, self-operated, dedicated server at NFOrce. Orchestrated, not virtualized.
        \item Ensured reliability, resilience, and performance through advanced linux features and Kernel-level tweaks.
        \item Managed deployment, resource allocation, and scalability by setting up MicroK8s cluster.
        \item Guaranteed security through firewall, IDS, IP whitelisting, PoLP, and auditing tools.    
        \item Implemented observability on system and service levels through monitoring, alerts, and dashboards.
        \item Averted impending hardware failures using low-level server metrics such as SMART data.
    \end{project}
\end{sectionList}
\section{Open-source Work}
\begin{itemList}
\item Founded multiple popular libraries and frameworks with contributors and strong userbases.
\item Mastered numerous problem domains ranging from parsing to algorithms to patching executables.
\item Ensured DevEx through strong API design, embraced by countless developers.
\item Achieved test coverage by building domain-specific test tools, as well as staples like mocking.
\item Implemented CI/CD pipelines and advanced repository and package configurations.
\item Maintained complex dependency trees and ensured compatibility across multiple versions.
\item Adminstered multiple repositories, managed contributions, and maintained quality standards.
\item Wrote comprehensive documentation, including tutorials, guides, and examples.
\end{itemList}
\begin{sectionList}
    \begin{project}{\textbf{\parjs} $|$ \emph{TypeScript, JavaScript} $|$ \https{\mycareersite/parjs}}{2018 -- Present}
        \item STATS LINE
        \item Translated Parsec's Haskell API to TypeScript, but tailored for the JS/TS ecosystem.
        \item Achieves DevEx using advanced TypeScript features and functional programming principles.
        \item Used by thousands of developers, including in production systems.
    \end{project}
    \begin{project}{\textbf{\patchwork} $|$ \emph{\sharplang{C}} $|$ \https{\mycareersite/Patchwork}}{X -- X}
        \item Framework for patching compiled .NET binaries for modding games that lack modding support.
        \item Hides technical binary transformations behind a friendly API.
        \item Enabled the development of countless mods by non-expert developers.
        \item The first of its kind, used as a model for contemporary tools.
        \item Peak userbase of 100+ developers, 100K+ end-users.
    \end{project}
\end{sectionList}
\section{Visa Notice}
\begin{itemList}
    \item I am an Israeli national. I seek to immigrate to the Netherlands due to political reasons.
    \item \textbf{I require a visa sponsorship} to work in the Netherlands.
    \item My intent is to permanently settle in the Netherlands with my partner and eventually naturalize.
\end{itemList}
\section{Languages}
\begin{itemList}
    \item \textbf{English:} Native-level proficiency.
    \item \textbf{Hebrew:} Native proficiency.
    \item \textbf{Russian:} Native language, but somewhat rusty.
\end{itemList}
%-------------------------------------------
\end{document}%
