
\begin{jobReflectizLead}
  \item Pivotal technical leadership position in a successful, rapidly growing client-side security company.
  \item Took charge of a monolithic system and scaled it to 100+ instances spread across 7 regions.
  \item Designed highly scalable and cost-effective systems based on input from key stakeholders, including:
    \begin{itemize}
      \item Cost-effective data pipeline processing over 300 MB/s of graph data.
      \item Development and automation platform used by a team of developers.
      \item A network of interdependent packages that accelerated
        development times.
    \end{itemize}
  \item Effectively communicated complex architectural
    characteristics to cross-functional teams.
  \item Accelerated development by:
    \begin{itemize}
      \item Increasing code reuse through refactoring existing
        codebases into a package architecture.
      \item Indentifying dev bottlenecks and writing automation tools
        to overcome them.
      \item Reviewing feature designs and specifications with an eye
        towards maintainability and scalability.
    \end{itemize}
  \item Used observability to ensure system performance and integrity by:
    \begin{itemize}
      \item Deploying a system-wide tracing solution, allowing for
        rapid incident response.
      \item Designing a suite of domain-specific system-wide metrics
        to monitor system health and performance.
      \item Building an accessible Grafana dashboard for cross-functional teams.
    \end{itemize}
  \item Enabled the acquisition of new clients by:
    \begin{itemize}
      \item Translating client demands into business requiments and
        research objectives.
      \item Leveraging IaC to expand into new regions.
      \item Participating in sales meetings with key clients as a
        technical expert.
    \end{itemize}
  \item Empowered developers to make architectural decisions by:
    \begin{itemize}
      \item Translating domain-specific stakeholder concerns into
        software requirements.
      \item Fostering open discussion about existing shortcomings,
        future needs, and potential solutions.
      \item Providing technical guidance and mentoring.
    \end{itemize}
  \item Research into incidents post-mortem, including:
    \begin{itemize}
      \item Root cause analysis and remediation.
      \item Translating highly technical information into actionable
        items for cross-functional teams.
      \item Drafted research findings for stakeholders and leaders --
        with an eye towards promotional material.
    \end{itemize}
  \item Set up CI/CD platforms and pipelines following GitOps principles:
    \begin{itemize}
      \item Deploying a system-wide tracing solution, allowing for
        rapid incident response.
      \item Designing a suite of domain-specific system-wide metrics
        to monitor system health and performance.
      \item Building an accessible Grafana dashboard for cross-functional teams.
      \item Research into incidents post-mortem, including root cause
        analysis and remediation.
    \end{itemize}
  \item Research into incidents post-mortem, including root cause
    analysis and remediation.
  \item Optimized RDBMS architecture using indexing and partitioning.
  \end{jobReflectizLead}