\section{Open-source Work}
\begin{itemList}
\item Founded multiple popular libraries and frameworks with
  contributors and strong userbases.
\item Mastered numerous problem domains ranging from parsing to
  algorithms to patching executables.
\item Ensured DevEx through strong API design, embraced by countless developers.
\item Achieved test coverage by building domain-specific test tools,
  as well as staples like mocking.
\item Implemented CI/CD pipelines and advanced repository and package
  configurations.
\item Maintained complex dependency trees and ensured compatibility
  across multiple versions.
\item Adminstered multiple repositories, managed contributions, and
  maintained quality standards.
\item Wrote comprehensive documentation, including tutorials, guides,
  and examples.
\end{itemList}
\begin{sectionList}
  \begin{project}{\textbf{\parjs} $|$ \emph{TypeScript, JavaScript}
    $|$ \https{\mycareersite/parjs}}{2018 -- Present}
  \item STATS LINE
  \item Translated Parsec's Haskell API to TypeScript, but tailored
    for the JS/TS ecosystem.
  \item Achieves DevEx using advanced TypeScript features and
    functional programming principles.
  \item Used by thousands of developers, including in production systems.
  \end{project}
  \begin{project}{\textbf{\patchwork} $|$ \emph{\sharplang{C}} $|$
    \https{\mycareersite/Patchwork}}{X -- X}
  \item Framework for patching compiled .NET binaries for modding
    games that lack modding support.
  \item Hides technical binary transformations behind a friendly API.
  \item Enabled the development of countless mods by non-expert developers.
  \item The first of its kind, used as a model for contemporary tools.
  \item Peak userbase of 100+ developers, 100K+ end-users.
  \end{project}
\end{sectionList}