\documentclass[a4paper,11pt]{article}

\input{./utils/_preamble.tex}
\input{./utils/_names.tex}
\newcommand{\eternitech}{Eternitech}
\newcommand{\reflectiz}{Reflectiz}
\newcommand{\appdome}{Appdome}
\newcommand{\sentto}{v }

 
\input{./utils/_eduenvs.tex}
\input{./utils/_jobenvs.tex}
\input{./points/_appdome.tex}
\input{./points/_eternitech.tex}
\input{./points/_ref.developer.tex}
\input{./points/_ref.architect.tex}
\begin{document}
\header%
\section{Experience}
\begin{sectionList}

  \begin{jobReflectizLead}
  \item Pivotal technical leadership position in a successful,
    rapidly growing client-side security company.
  \item Took charge of a monolithic system and scaled it to 100+
    instances spread across 7 regions.
  \item Designed highly scalable and cost-effective systems based on
    input from key stakeholders, including:
    \begin{itemize}
      \item Cost-effective data pipeline processing over 300 MB/s of graph data.
      \item Development and automation platform used by a team of developers.
      \item A network of interdependent packages that accelerated
        development times.
    \end{itemize}
  \item Effectively communicated complex architectural
    characteristics to cross-functional teams.
  \item Accelerated development by:
    \begin{itemize}
      \item Increasing code reuse through refactoring existing
        codebases into a package architecture.
      \item Indentifying dev bottlenecks and writing automation tools
        to overcome them.
      \item Reviewing feature designs and specifications with an eye
        towards maintainability and scalability.
    \end{itemize}
  \item Used observability to ensure system performance and integrity by:
    \begin{itemize}
      \item Deploying a system-wide tracing solution, allowing for
        rapid incident response.
      \item Designing a suite of domain-specific system-wide metrics
        to monitor system health and performance.
      \item Building an accessible Grafana dashboard for cross-functional teams.
    \end{itemize}
  \item Enabled the acquisition of new clients by:
    \begin{itemize}
      \item Translating client demands into business requiments and
        research objectives.
      \item Leveraging IaC to expand into new regions.
      \item Participating in sales meetings with key clients as a
        technical expert.
    \end{itemize}
  \item Empowered developers to make architectural decisions by:
    \begin{itemize}
      \item Translating domain-specific stakeholder concerns into
        software requirements.
      \item Fostering open discussion about existing shortcomings,
        future needs, and potential solutions.
      \item Providing technical guidance and mentoring.
    \end{itemize}
  \item Research into incidents post-mortem, including:
    \begin{itemize}
      \item Root cause analysis and remediation.
      \item Translating highly technical information into actionable
        items for cross-functional teams.
      \item Drafted research findings for stakeholders and leaders --
        with an eye towards promotional material.
    \end{itemize}
  \item Set up CI/CD platforms and pipelines following GitOps principles:
    \begin{itemize}
      \item Deploying a system-wide tracing solution, allowing for
        rapid incident response.
      \item Designing a suite of domain-specific system-wide metrics
        to monitor system health and performance.
      \item Building an accessible Grafana dashboard for cross-functional teams.
      \item Research into incidents post-mortem, including root cause
        analysis and remediation.
    \end{itemize}
  \item Research into incidents post-mortem, including root cause
    analysis and remediation.
  \item Optimized RDBMS architecture using indexing and partitioning.
  \end{jobReflectizLead}

  \begin{jobAppdome}
    \AppSummaryTechLead
    \AppGuidedDevelopers
    \AppComplexTechnical
    \AppModernizedDevelopmentProcesses
    \AppMajorRefactoring
  \end{jobAppdome}

  \begin{jobReflectizDev}
    \RefDevFoundational
    \RefDevDevelopment
    \RefDevOptimized
  \end{jobReflectizDev}
  \begin{jobEternitech}
    \EtrSPAsForClients
    \EtrMaintainedExistingApps
    \EtrRequirementsAndSpecifications
  \end{jobEternitech}
\end{sectionList}%

\section{Education}
\begin{sectionList}
  \begin{eduTechnion}
  \end{eduTechnion}
\end{sectionList}%
%-----------PROJECTS-----------
\section{Own Work}
\begin{sectionList}
  \begin{project}{\textbf{\gregrosdev} $|$ Blog $|$
    \https{\mywebsite}}{2024 -- Present}
  \item A software development and architecture blog.
  \item Posta about web technologies, JS engines, API design, and architecture.
  \item Conveys complex ideas using a simple and informal tone.
  \item Grew readership and engagement using marketing principles.
  \item Hosted on \textbf{gregros.dev (platform)}.
  \end{project}
  \begin{project}{\textbf{\gregrosdev} $|$ Platform $|$
    \textit{Next.js, React, TypeScript, SCSS}}{2024 -- Present}
  \item Content platform built using industry-leading web technologies.
  \item Integrated marketing staples like Google Analytics, SEO, and social.
  \item Deployed via CD pipeline on \textbf{Laniakea (Cluster)}.
  \end{project}
  \begin{project}{\textbf{\laniakea} $|$ Cluster $|$ \textit{k8s,
        OCI, Flux, k0s, MetalLB, GitOps Weave, Traefik, k8s
    Gateway}}{2023 -- Present}
  \item Bare-metal k8s cluster (k0s) built with industry-leading
    open-source technologies.
  \item Highly observable through dashboards (GitOps Weave, K8s dash)
    and tools (k9s, kubectl, kubeq).
  \item Achieves high performance by avoiding virtualization overhead.
  \item Hosts numerous services and platforms, including \textbf{gregros.dev}.
  \item All resources managed in SCM following GitOps principles,
    reconciled using Flux.
  \item Avoids vendor lock-in through pure k8s solutions, e.g.
    cutting-edge Gateway API.
  \item Network exposure managed by industry-leading load balancing
    solutions (MetalLB, wg VPN)
  \item Secured through namespaces, policy-based network isolation, and PoLP.
  \item Deployed on \textbf{Laniakea (server)}.
  \end{project}
  \begin{project}{\textbf{\laniakea} $|$ Server $|$ \textit{Debian,
    Bash, SSH, iLO, }}{2022 -- Present}
  \item Enterprise-grade, rack-mounted, dedicated server --
    administered via SSH and HP iLO.
  \item Tuned for high performance through advanced Linux features
    and Kernel-level tweaks.
  \item Resiliency through RAID 1, regular backups, and system-level
    observability.
  \item Hardened using FW, VPN (wg), IDS (Snort), auditing (NMap), PoLP.
  \item Experienced and recovered from hardware failure and data loss.
  \end{project}
\end{sectionList}
\section{Open-source Work}
\begin{itemList}
\item Founded multiple popular libraries and frameworks with
  contributors and strong userbases.
\item Mastered numerous problem domains ranging from parsing to
  algorithms to patching executables.
\item Ensured DevEx through strong API design, embraced by countless developers.
\item Achieved test coverage by building domain-specific test tools,
  as well as staples like mocking.
\item Implemented CI/CD pipelines and advanced repository and package
  configurations.
\item Maintained complex dependency trees and ensured compatibility
  across multiple versions.
\item Adminstered multiple repositories, managed contributions, and
  maintained quality standards.
\item Wrote comprehensive documentation, including tutorials, guides,
  and examples.
\end{itemList}
\begin{sectionList}
  \begin{project}{\textbf{\parjs} $|$ \emph{TypeScript, JavaScript}
    $|$ \https{\mycareersite/parjs}}{2018 -- Present}
  \item STATS LINE
  \item Translated Parsec's Haskell API to TypeScript, but tailored
    for the JS/TS ecosystem.
  \item Achieves DevEx using advanced TypeScript features and
    functional programming principles.
  \item Used by thousands of developers, including in production systems.
  \end{project}
  \begin{project}{\textbf{\patchwork} $|$ \emph{\sharplang{C}} $|$
    \https{\mycareersite/Patchwork}}{X -- X}
  \item Framework for patching compiled .NET binaries for modding
    games that lack modding support.
  \item Hides technical binary transformations behind a friendly API.
  \item Enabled the development of countless mods by non-expert developers.
  \item The first of its kind, used as a model for contemporary tools.
  \item Peak userbase of 100+ developers, 100K+ end-users.
  \end{project}
\end{sectionList}
\section{Visa Notice}
\begin{itemList}
\item I am an Israeli national. I seek to immigrate to the
  Netherlands due to political reasons.
\item \textbf{I require a visa sponsorship} to work in the Netherlands.
\item My intent is to permanently settle in the Netherlands with my
  partner and eventually naturalize.
\end{itemList}
\section{Languages}
\begin{itemList}
\item \textbf{English:} Native-level proficiency.
\item \textbf{Hebrew:} Native proficiency.
\item \textbf{Russian:} Native language, but somewhat rusty.
\end{itemList}
%-------------------------------------------
\end{document}%
